Medical Concept Extraction

### 2012-12-16 paper/paper.tex

\subsubsection{Linear SVMs}
There are some large data for which with/without nonlinear mappings gives similar performances. Without using kernels, one can quickly train a much larger set via a linear classifier.

Clarification: liblinear is not doing linear regression, the default is L2-regularized SVM solver using L2-loss SVC in the dual.

>>>>

We tested a non-linear SVM as provided by the open-source library, LibSVM \cite{libsvm}.

\subsubsection{Linear SVMs}
As mentioned previously, we cannot always expect linearly separable training data. However, for large enough data sets, linear SVMs and SVMs with nonlinear mappings yield similar performance. By eliminating the need for a kernel mapping, training becomes much less costly through use of a linear support vector machine.

We additionally tested a strictly linear SVM using the open-source library, LibLinear \cite{liblinear}, which provides an L2-loss linear SVM solver.
